<br>

# Exploring data of Beer Supply and Demand 

This page is meant for you, as a brewer, to guide your decision about which beers to brew, from style, to ABV, to IBU, and where the best places are to market and sell your brew.
Once you're done exploring move on to the Predict tab so see how we think your beer will do in different markets.

<br>

### Beer consumption in the U.S.

This app shows where Untappd users are drinking different styles of beer, and is based on check-in data from [Untappd](https://untappd.com). 

Untappd users tend to be more heavily located on the U.S. coastal states, but you 
should still be able to still some unique differences amound beer style preferences 
among different regions of the country.  

<iframe src="./Capstone Dashboard/" style="border: 1px solid #FFF; width: 900px; height: 700px"></iframe>

<br>

### Users' Preference by Brewery State

The choropleth map below highlights the states with the highest rated beers. 
While the total range in mean rating between states is pretty small, it is still 
fun to take pride in knowing your home state brews some *mean* beers. 

```{r rating_map, echo=FALSE, warning=FALSE}
library(choroplethr)
bp_by_state = read.csv("bp_rating_by_state.csv", stringsAsFactors = FALSE)
state_choropleth(bp_by_state, 
                   title = "Mean BeerPal Rating of Beers by State Brewed In",
                   legend = "Mean Beer Rating",
                   num_colors = 5)
```

### Top Beers 

The "rating" is average score of a Likert scale from 1 to 5, with 1 being "poor" 
and 5 being "great". The "reviews" are how many times that beer was rated.

```{r datatable, echo=FALSE, warning=FALSE}
bp = read.csv("bp_ratings.csv", stringsAsFactors = FALSE)
bp = bp[, c(10, 3, 5, 6, 8, 9)]
DT::datatable(bp)
```

<br>
