<br>

# Exploring data of Beer Supply and Demand 

This page is meant for you, as a brewer, to guide your decision about which beers to brew, from style, to ABV, to IBU, and where the best places are to market and sell your brew.
Once you're done exploring move on to the Predict tab so see how we think your beer will do in different markets.

<br>

### Beer consumption in the U.S.

This app shows where Untappd users are drinking different styles of beer, and is based on check-in data from [Untappd](https://untappd.com). 

Untappd users tend to be more heavily located on the U.S. coastal states, but you 
should still be able to still some unique differences amound beer style preferences 
among different regions of the country.  

<iframe src="./Capstone Dashboard/" style="border: 1px solid #FFF; width: 900px; height: 700px"></iframe>

<br>

### Preference by Brewery State

The choropleth map below highlights the states with the highest rated beers. 
While the total range in mean rating between states is pretty small (3.62 to 3.88), 
by [standardizing the ratings using a Z-transformation](https://en.wikipedia.org/wiki/Standard_score) 
we can see that there are a handful of states producing the craft beers preferred by beer connoisseurs. 

To interpret the standard scores below, use this guide:

- A score of 0 tells us the average beer coming from that state was rated exactly the same as the national average
- A score of 1 tells us the average beer coming from that state was rated one standard deviation higher than the national average, so think top 84%
- A score of 2 tells us the average beer coming from that state was rated two standard deviations higher than the national average, so think top 98%
- Likewise, a score of -1 tells us the average beer coming from that state was rated one standard deviation below than the national average, or bottom 16%

This state level data also shows us a bit of the regional biases embedded in online reviews. 
Not coincidentally, the states with the most reviews also tend to have the highest ratings. 

All these statistics aside, it is still fun to take pride in knowing your home state brews some *mean* beers. 

<br> 

#### **Standardized Ratings from BeerPal.com by Brewery State**

```{r rating_map, include=FALSE}
bp_by_state = read.csv("bp_rating_by_state.csv", stringsAsFactors = FALSE)
bp_by_state = bp_by_state[,1:2]
bp_by_state$rating = round(bp_by_state$rating, 3)
missing_states = data.frame(state=c("NV", "ND", "SD", "IA", "AR", "MS", "KY", "WV"),
                            rating=rep(min(bp_by_state$rating, 8)))
state_ratings = rbind(bp_by_state, missing_states)
state_ratings[state_ratings$state=="RI",] = c("RI", 3.62)
state_ratings$rating = as.numeric(state_ratings$rating)
state_ratings$z_score = scale(state_ratings$rating)
```


```{r, echo=FALSE, results='asis', comment=NA}
library(rMaps)
# bpmap = rMaps::ichoropleth(rating ~ state, data = state_ratings, 
#                            legend = TRUE, labels = TRUE, 
#                            ncuts = 6, pal = "PuBuGn")
# bpmap$set(geographyConfig = list(
#     popupTemplate = "#! function(geography, data){
#       return '<div class=hoverinfo><strong>' + geography.properties.name + 
#       ': ' + data.rating + '</strong></div>';
#     } !#"
# ))
bpmap = rMaps::ichoropleth(z_score ~ state, data = state_ratings,
                           legend = TRUE, labels = TRUE, 
                           ncuts = 6, pal = "BuGn")
bpmap$set(geographyConfig = list(
    popupTemplate = "#! function(geography, data){
      return '<div class=hoverinfo><strong>' + geography.properties.name + 
      ': ' + data.z_score + '</strong></div>';
    } !#"
))
#bpmap
bpmap$print('chart2', include_assets = TRUE, cdn = TRUE)
```

<br>

*The legend is grouped into 6 even buckets by frequency of occurence, not even breaks between standard scores.*

<br>

### Top Beers 

The "rating" is average score of a Likert scale from 1 to 5, with 1 being "poor" 
and 5 being "great". The "reviews" are how many times that beer was rated.

```{r datatable, echo=FALSE, warning=FALSE}
bp = read.csv("bp_ratings.csv", stringsAsFactors = FALSE)
bp = bp[, c(10, 3, 5, 6, 8, 9)]
DT::datatable(bp, filter = "top")
```

<br>
