<br>

# Exploring data of Beer Supply and Demand 

This page is meant to guide you through the data publicly available regarding
beer in as visual and interactive way possible. 

<br>

# Untappd

**Socially media for beer drinkers, check it out at [Untappd](https://untappd.com)**

> Untappd is a new mobile web app that allows you to socially share the brew you're currently enjoying, as well as where you're enjoying it, with your friends!

This app shows where Untappd users are drinking different styles of beer. 
Untappd users tend to be more heavily located on the U.S. coastal states, but you 
should still be able to still some unique differences amound beer style preferences 
among different regions of the country.  

<iframe src="./Capstone Dashboard/" style="border: 1px solid #FFF; width: 900px; height: 600px"></iframe>

<br>

# FRED

**From the [Economic Research Division of the Federal Reserve Bank of St. Louis](https://research.stlouisfed.org/docs/api/fred/fred.html)**

> FRED速 stands for Federal Reserve Economic Data. FRED速 contains frequently updated US macro and regional economic time series at annual, quarterly, monthly, weekly, and daily frequencies. FRED速 aggregates economic data from a variety of sources- most of which are US government agencies. The economic time series in FRED速 contain observation or measurement periods associated with data values. For instance, the US unemployment rate for the month of January, 1990 was 5.4 percent and for the month of January, 2000 was 4.0 percent.

We used the FRED API to extract data on the supply and sales of beer over a 20 year period,
as well as price indices for breweries.

<br>

## Brewery Price Indices

### What is a Price Index?

**From the [Bureau Of Labor Statistics](http://www.bls.gov/ppi/data.htmhttp://www.bls.gov/ppi/data.htm)**

> The Producer Price Index (PPI) program measures the average change over time in 
> the selling prices received by domestic producers for their output. The prices 
> included in the PPI are from the first commercial transaction for many products 
> and some services.

The data on price indices shows PPI for several different goods produced by breweries. 
A PPI always has an initial date at which the index began. 
This index date is usually when the agency recording began
collecting data and is set to 100 for each of the categories below. 
The index date for each category below is June 1, 1982.

```{r prepare_date, include=FALSE}
library(dygraphs)
library(xts)
fred_idx = read.csv("fred_idx.csv")
fred_idx = fred_idx[, c(1, 2, 4, 5, 6)]
fred_idx$index_date = as.Date(fred_idx$index_date)
colnames(fred_idx) = c("index_date", "cases_bottles", "cases_cans", "barrels_and_kegs", "overall")
fred_idx = as.xts(fred_idx[, 2:5], order.by = fred_idx[, 1])
```

```{r ts_graph_idx, echo=FALSE, warning=FALSE}
dygraph(fred_idx, main = "Brewery Price Index Data") %>%
  dyLegend(width = 600) %>%
  dyRangeSelector()
```

<br><br>

# BeerPal

According to [BeerPal.com](http://www.beerpal.com/)

> BeerPal is the most user friendly beer community in the world; a resource of beers, breweries, events and news with reviews and ratings.

BeerPal has been collecting reviews on beers from users to build a list of the 
[Top Beers](http://www.beerpal.com/Best-Beer.htm).

The charts below highlight some interesting aspects about how the internet rates beers.

### BeerPal User Submission Distributions 

Use this app to explore how BeerPal.com users rate beers of different styles and 
the states those beers came from. The category "rating" is a Likert scale from 1 to 5, 
with 1 being "poor" and 5 being "great". The category "reviews" counts how many times 
a rating was submitted for the given combination of inputs.  

*Please note that not all combinations have data. If you see an error message about invalid breaks, just try a different pair*  

<iframe src="./BeerPal/" style="border: 1px solid #FFF; width: 900px; height: 600px"></iframe>


```{r rating_map, echo=FALSE, warning=FALSE}
library(choroplethr)
bp_by_state = read.csv("bp_rating_by_state.csv", stringsAsFactors = FALSE)
state_choropleth(bp_by_state, 
                   title = "Mean BeerPal Rating of Beers by State Brewed In",
                   legend = "Mean Beer Rating",
                   num_colors = 5)
```


