<br>

# Predicting the Demand of Beer Styles
*Capstone project for UC Berkeley MIDS, Sping 2016*

**Ray Buhr, Carson Forter, Satish Terala**

<br>

## GOAL:
### Help brewers make the right beer in the right place at the right time.

<br>

## But Why Beer Models?

- Big industry
- Major year-over-year growth
- Few players in the data/beer space
- New players need data to succeed and represent an opportunity

<br>

## Brewery Supply and Demand

According to the data available through the [Economic Research Division of the Federal Reserve Bank of St. Louis](https://research.stlouisfed.org/docs/api/fred/fred.html), 
the total inventory of beer has grown fairly linearly over the last 20+ years. 
The sales of beer has grown as well, but not matching the inventory quite exactly.  

In the chart below, notice the seasonality in the sales of beer as each year, especially  
that the months of January and February dip greatly from the peak months of November 
and December. Starting about 2007 you can also see that inventory starts growing 
faster than sales, which corresponds to beginning of the rise of craft and micro breweries 
popping up accross the country.  

```{r prepare_sales, include=FALSE}
library(dygraphs)
library(xts)
fred_sales = read.csv("FRED_inventory_sales.csv")
fred_sales = fred_sales[, c(2, 3, 4)]
fred_sales$month = as.Date(fred_sales$month)
fred_sales = as.xts(fred_sales[, 2:3], order.by = fred_sales[, 1])
```

```{r ts_graph_sales, echo=FALSE, warning=FALSE}
dygraph(fred_sales, main = "Brewery Supply and Demand") %>%
  dyLegend(width = 600) %>%
  dyRangeSelector()
```

<br>

## Data Science Approach

**Get data**

- Sales data and consumption data from various sources
- Untappd, OpenBeerDB, FRED, Twitter

**Clean and transform data**

- Load all data into uniform RDBMS

**Explore**

- Do exploratory analysis to understand correlations and trends

**Model**

- Build and test various models to predict ratings, sentiment, and consumption location, including multiple models by style and location

**Present and polish**

- Visualize models in a Shiny dashboard for breweries to use

<br>

## Next Steps

- Add sentiment aggregated by style to supplement maps
- Adapt style model to account for regional biases in data 
- Keep looking for new data sources to incorporate
- Get more feedback from breweries of what problems they have that data science can solve